devtools::install_github("ropensci/plotly")


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, echo = FALSE, 
                      message = FALSE, warning = FALSE)
```

## Introduction

- This project was created as part of the Developing Data Products course of the Coursera [Data Science Specialisation](https://www.coursera.org/specializations/jhu-data-science).

- The goal of the project is to create a web page presentation using R Markdown that features a plot created with Plotly, and to host the resulting web page on either GitHub Pages, RPubs, or NeoCities.

- The interactive plot on the next slide represents the number of road accidents in Great Britain from 2005 to 2015, grouped by severity (slight, serious, or fatal).

    + A Loess smoother line has been added to highlight the overall evolution of the number of accidents.


```{r prerequisites}
rm(list=ls())
library(plotly)
library(data.table)
library(tidyr)
library(lubridate)
library(zoo)
```

```{r load_data, results='hide'}
f <- list(
  family = "Courier New, monospace",
  size = 11,   color = "#6e6e6e" )
x <- list(
  title = "Weight (1000 lbs)",   titlefont = f )

y <- list(
  title = "Mileage per gallon",   titlefont = f )
plot_ly(mtcars, x = mtcars$wt, y=mtcars$mpg, mode="markers", 
        type="scatter",color=as.factor(mtcars$cyl), size=mtcars$hp ) %>%   
        layout(xaxis=x, yaxis=y)
